\documentclass[9pt,a4paper,withhyper]{altacv}

\geometry{left=1.2cm,right=1.2cm,top=1.8cm,bottom=1.2cm,columnsep=1cm}

% for columns
\usepackage{paracol}

% If using pdflatex:
\usepackage{charter}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }

\urlstyle{same}


% Change the colours if you want to
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
% \colorlet{name}{black}
\colorlet{tagline}{VividPurple}
\colorlet{heading}{VividPurple}
\colorlet{headingrule}{VividPurple}
% \colorlet{subheading}{PastelRed}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change some fonts, if necessary
% \renewcommand{\namefont}{\Huge\rmfamily\bfseries}
% \renewcommand{\personalinfofont}{\footnotesize}
% \renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
% \renewcommand{\cvsubsectionfont}{\large\bfseries}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{Aaron William Po \\ \large{\vspace{-1em} full stack developer}}

\personalinfo{%
  \email{aaron\_po@msn.com}
  \location{London, ON}
  \github{github.com/aaronpo97}
  \faDesktop\,\,
  \url{aaronwilliampo.com}
}
\makecvheader
\columnratio{0.55}

\begin{paracol}{2}
  \cvsection{About}
  I am a developer specializing in Typescript/Javascript development with a passion for creating versatile applications for both client and server environments. Committed to continuous learning and innovation, I thrive in dynamic work environments that foster growth and encourage collaboration. I am eager to contribute my skills and expertise to a team's success while further expanding my knowledge in the field.

  \cvsection{Projects}
  \cvevent{The Biergarten App}{\faCode \,Next.js, Prisma, Postgres, Tailwind CSS}{\url{https://github.com/aaronpo97/the-biergarten-app}}{}
  \begin{itemize}
	\item An innovative web application designed for beer enthusiasts to connect and share their favorite brews and breweries online, that allows beer lovers to engage with like-minded individuals, discussing and discovering new beer experiences.
    \item Leverages the power of \textbf{Next.js}, \textbf{Prisma}, and \textbf{Neon Postgres} to create a dynamic web application focused on fostering a passionate beer community.
    \item Integrates APIs such as \textbf{Cloudinary}, \textbf{SparkPost}, and \textbf{Mapbox} to enrich the user experience by enabling functionalities like image uploading, email services, and geolocation features.
    \item Uses \textbf{Tailwind CSS}, \textbf{Headless UI}, and \textbf{Daisy UI} to create a visually striking and user-friendly interface, enhancing the overall user experience.
    \item Deployed with \textbf{Vercel} for its fast and seamless deployment process that integrates directly with \textbf{Next.js}.
  \end{itemize}

  \divider

  \cvevent{SpoonBot}{\faCode \, Technologies: Next.js, Tailwind CSS, OpenAI}{\url{https://github.com/aaronpo97/spoonbot}}{}
  \begin{itemize}
    \item Spearheaded the development of SpoonBot, a cutting-edge web application powered by OpenAI's \textbf{GPT-3 API}, showcasing its ability to generate restaurant names, detailed restaurant reviews, and enticing restaurant menus.
    \item Implemented robust content moderation features to ensure a safe and respectful user experience, leveraging advanced techniques to detect and prevent offensive or harmful language in user input.
    \item Crafted a visually stunning and responsive user interface by harnessing the power of \textbf{Next.js}, a React-based framework, and seamlessly integrating it with the versatility of \textbf{Tailwind CSS}.
    \item Deployed with \textbf{Vercel} for its fast and seamless deployment process that integrates directly with \textbf{Next.js}.
  \end{itemize}

  \switchcolumn

  \cvsection{Education}
  \cvevent{\faSchool \, University of Western Ontario}{London, Ontario, Canada}{2020}{}
  \begin{itemize}
    \item Bachelor of Music
  \end{itemize}

  \cvsection{Courses taken}
  \cvevent{The Web Developer Bootcamp}{instructed by Colt Steele, udemy.com}{2021}{}

  \begin{itemize}
    \item Certificate of Completion
  \end{itemize}
  \cvsection{Skills}
  \cvevent{\faCode \, Core Competencies}{}{}{}
  \begin{itemize}
    \item Quickly learns and applies new technologies and methodologies.
    \item Efficiently manages time, prioritizes tasks, and meets deadlines.
    \item Applies critical thinking skills to evaluate situations and make informed decisions.
    \item Self-motivated and takes initiative for personal and professional growth.
    \item Committed to continuous learning and staying updated with industry trends.
    \item Adapts to changing project requirements and embraces new methodologies.
  \end{itemize}
  \divider
  \cvevent{\faCode \, Web and Mobile Development}{}{}{}
  \begin{itemize}
    \item Proficient in \textbf{React} for client-side web applications and \textbf{React Native} for mobile app development.
    \item Strong understanding of front-end principles: \textbf{responsive design}, \textbf{accessibility}, and \textbf{performance optimization}.
    \item Skilled in \textbf{Next.js} and \textbf{Redux} for modern web development.
    \item Experienced with UI component libraries (\textbf{Material-UI}, \textbf{Mantine}) and CSS frameworks (\textbf{Bootstrap}).
    \item Proficient in \textbf{Tailwind CSS} for rapid UI development and customization.
    \item Familiar with back-end concepts and tools \textbf{RESTful APIs}, \textbf{Node.js}, \textbf{Express}.
    \item Strong problem-solving and debugging skills.
    \item Proficient in \textbf{Git} for version control (\textbf{GitHub} collaboration).
    \item Experienced with \textbf{Linux} (Bash scripting) and \textbf{Mac OS} development tools.
  \end{itemize}

\end{paracol}

\end{document}